---
title: "npillana_QMM-5"
date: "11/5/2021"
output:
  word_document: default
  html_document: default
---

## Loading required libraries
```{r}

library(Benchmarking)
library(lpSolveAPI)

```
 

```{r}

DMU1<- read.lp("C:/Users/nihar/OneDrive/Desktop/Fall Assignments/QMM/Assignment 5/DMU1.lp")
DMU1
solve(DMU1)
get.objective(DMU1)
get.variables(DMU1)

```

The lp is able to acheive maximum efficiency 1 for DMU1.
The proposed inputs and outputs when we use the weights 5.17 and 
1.12 for the outputs, 7.14 and 0.00 for the input for maximum efficiency.

```{r}

DMU2<- read.lp("C:/Users/nihar/OneDrive/Desktop/Fall Assignments/QMM/Assignment 5/DMU2.lp")
DMU2
solve(DMU2)
get.objective(DMU2)
get.variables(DMU2)

```
The lp is able to acheive maximum efficiency 1 for DMU2.
The proposed inputs and outputs when we use the weights 1.29 and 
6.8 for the outputs, 0.00 and 4.7 for the input for maximum efficiency.

```{r}

DMU3<- read.lp("C:/Users/nihar/OneDrive/Desktop/Fall Assignments/QMM/Assignment 5/DMU3.lp")
DMU3
solve(DMU3)
get.objective(DMU3)
get.variables(DMU3)

```
The lp is able to acheive maximum efficiency 1 for DMU3.
The proposed inputs and outputs when we use the weights 1.7 and 
3.7 for the outputs, 2.3 and 0.00 for the input for maximum efficiency.

```{r}

DMU4<- read.lp("C:/Users/nihar/OneDrive/Desktop/Fall Assignments/QMM/Assignment 5/DMU4.lp")
DMU4
solve(DMU4)
get.objective(DMU4)
get.variables(DMU4)

```
The lp is able to acheive efficiency 0.98 with DMU4.
The proposed inputs and outputs when we use the weights 1.9 and 
0.0 for the outputs, 1.05 and 1.63 for the input for maximum efficiency.
Even though we provide the greatest weight to deposits, DMU4 is not efficient.

```{r}

DMU5<- read.lp("C:/Users/nihar/OneDrive/Desktop/Fall Assignments/QMM/Assignment 5/DMU5.lp")
DMU5
solve(DMU5)
get.objective(DMU5)
get.variables(DMU5)

```
The lp is able to achieve efficiency 0.96 for DMU5.
The proposed inputs and outputs when we use the weights 1.03 and 5.3 for the outputs, 1.11 and 2.99 for the input for maximum efficiency.
Even though we provide the greatest weight to deposits, DMU5 is not efficient.

```{r}

DMU6<- read.lp("C:/Users/nihar/OneDrive/Desktop/Fall Assignments/QMM/Assignment 5/DMU6.lp")
DMU6
solve(DMU6)
get.objective(DMU6)
get.variables(DMU6)

```
The lp is able to acheive efficiency 0.86 for DMU6.
The proposed inputs and outputs when we use the weights 1.46 and 7.56 for the outputs, 1.59 and 4.26 for the input for maximum efficiency.
Even though we provide the greatest weight to deposits, DMU6 is not efficient.


First we will define our inputs and outputs as vectors . we have 2 inputs (Staff hours, Supplies) and 2 outputs(“Reimbursed Patient_Days”,"Privately Paid Patient_Day)

```{r}

x <- matrix(c(150, 400, 320, 520, 350, 320, 0.2, 0.7, 1.2, 2.0, 1.2, 0.7), ncol = 2)
y <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000),ncol = 2)
colnames(x) <- c("Staff_Hours", "Supplies")
colnames(y) <- c("Reimbursed Patient_Days","Privately Paid Patient_Days")
print(x)
print(y)
Matrix<- cbind(x,y)
row.names(Matrix) = c("Faci1", "Faci2", "Faci3", "Faci4", "Faci5", "Faci6")
Matrix

```
# Formulate and perform DEA analysis under all DEA assumptions of FDH, CRS, VRS, IRS, DRS, and FRH.

```{r}

#Free disposability hull
FDH <- dea(x,y, RTS = "fdh")
FDH
peers(FDH)
FDH_Weights <- lambda(FDH)

```
The peer for each facility is same as the peer.

```{r}

#Constant returns to scale, convexity and free disposability
CRS <- dea(x,y, RTS = "crs")
CRS
#Identify Peers
peers(CRS)
#Identify lambda
CRS_Weights <- lambda(CRS)

```
The results show DMU 1,2,3,4 are efficient and DMU 5 is 0.9775, DMU 6 0.867
The peer for 5 and 6 are 1,2,3

```{r}

#Variable returns to scale, convexity and free disposability
VRS <- dea(x,y, RTS = "vrs")
VRS
peers(VRS)
VRS_Weights <- lambda(VRS)

```
All facilities are efficient except DMU5 which is 0.8963.
The peer for 6 are 1,2,5

```{r}

#Increasing returns to scale, (up-scaling, but not down-scaling), convexity and free disposability
IRS <- dea(x,y, RTS = "irs")
IRS
peers(IRS)
IRS_Weights <- lambda(IRS)

```
All facilities are efficient except DMU5 which is 0.8963.
The peer for 6 are 1,2,5

```{r}

#Decreasing returns to scale, convexity, down-scaling and free disposability
DRS <- dea(x,y, RTS = "drs")
DRS
peers(DRS)
DRS_Weights <- lambda(DRS)

```
The results show DMU 1,2,3,4 are efficient and DMU 5 is 0.9775, DMU 6 0.867
The peer for 5 and 6 are 1,2,4

```{r}

FRH <- dea(x,y, RTS="add")
FRH
peers(FRH)
FRH_Weights <- lambda(FRH)

```
All facilities are efficient.
The peer for each facility is same as the peer.

```{r}

as.data.frame(Matrix)
DataFrame<- data.frame(CRS = c(1.0000, 1.0000, 1.0000, 1.0000, 0.9775, 0.8675), FDH = c(1, 1, 1 ,1 ,1 ,1), VRS =c(1.0000, 1.0000, 1.0000, 1.0000 ,1.0000, 0.8963), IRS = c(1.0000, 1.0000, 1.0000, 1.0000, 1.0000, 0.8963), DRS = c(1.0000, 1.0000, 1.0000 ,1.0000 ,0.9775, 0.8675), FRH = c(1, 1, 1 ,1, 1, 1))
DataFrame

```
From the above output the Facilities 1,2,3,4 are fully efficient for all the assumptions and Facilities 5,6 are not efficient.
Facility 5 is fully efficient for FDH, VRS, IRS and FRH assumptions.
It is observed that 97.7% efficient for CRS and DRS assumptions.
Facility 6 is fully efficient for FDH and FRS assumptions.
For Facility 6 CRS and DRS assumptions 86.7% efficient.
For Facility 6 IRS and VRS assumptions 89.6% efficient.

### DEA Analysis Summary for Hope Vally Health Care Association: Under FDH and FRH all facilities are efficient

# Question 2 : GOAL PRORAMMING

Maximize Z = P - 6C - 3D, where
P = total (discounted) profit over the life of the new products,
C = change (in either direction) in the current level of employment,
D = decrease (if any) in next year’s earnings from the current year’s level.

Profit P is defined as:
P = 20x1 +15x2 + 25x3

Employment level is defined as :
6x1 + 4x2 + 5x3 = 50

Next year Earnings goal is defined as:
8x1 + 7x2 + 5x3 >=75

# 1) Model_Formulation:

Let us consider
y1 - Employment Level minus the target and
y2 - Next Year Earnings minus the Target
y1+ - Penalty for employment level goal exceeding 50
y1- - Penalty for employment level goal decreasing below 50
y2+ - Exceed the next year earnings
y2- - Penalty for not reaching the next year earnings

y1 = 6x1 + 4x2 + 5x3 - 50
y2 = 8x1 + 7x2 + 5x3 -75

### For Employment level goal
y1 = y1+ - y1- where y1+, y1- >=0
y1+ - y1-= 6x1 + 4x2 + 5x3 - 50

### For Next year earnings goal
y2 = y2+ - y2- where y2+, y2- >=0
y2+ - y2- = 8x1 + 7x2 + 5x3 -75

### Final Formulation is expressed as
Max P = 20x1 +15x2 + 25x3
6x1 + 4x2 + 5x3 - (y1+ - y1-) = 50
8x1 + 7x2 + 5x3 - (y2+ - y2-) = 75

Where, xj >=0, where j=1,2,3
       yi + >=0, where i= 1,2
       yi - >=0, where i= 1,2

# 2)Managements objective function Objective Function

Maximize Z = P - 6C - 3D

Objective function in terms of x1, x2, x3, y1+, y1- , y2+ and y2-
Max Z = 20x1 +15x2 + 25x3 - 6y1+ - 6y1- - 3y2-
6x1 + 4x2 + 5x3 - (y1+ + y1-) = 50
8x1 + 7x2 + 5x3 - (y2+ + y2-) = 75
Where, xj >=0 where j=1,2,3
       yi + >=0 where i= 1,2
       yi - >=0 where i= 1,2

# 3) Formulate and solve the linear programming model

```{r}

GoalProgram<- read.lp("C:/Users/nihar/OneDrive/Desktop/Fall Assignments/QMM/Assignment 5/Emax.lp")
GoalProgram
solve(GoalProgram)
get.objective(GoalProgram)
get.variables(GoalProgram)
get.constraints(GoalProgram)

```

The penalty is 225 if you are not satisfying the goals on the objective function.
The results show that 
x1 = 0, 
x2 = 0, 
x3 = 15, 
y1+ = 25, 
y1− = 0, 
y2+ = 0, 
y2− = 0, 
which explains the Next years Earnings (y2) expectations are fully satisfied.
Emax need to produce 15 units of product 3 and none of product 1 and 2 to achieve 225 millions in profit.
